Fractional Decomposition Tree Algorithm: A tool for studying the integrality gap of Integer Programs

### 2022-01-31 FDT2020/Introduction.tex
addressed the issue w. adding constraints

It is  NP-hard even to determine if an IP instance has a feasible solution~\cite{GareyJohnson}. Given its practical importance, however, there are many commercial (e.g. CPLEX, GUROBI, XPRESS) and free (e.g. CBC) solvers that for specific IP instances can often find solutions that are optimal within a given tolerance. Still there are known moderate-sized IP instances that no commercial solver can currently solve \cite{MIPLIB}. Thus there is value in heuristics to find feasible solutions for general IP instances (see e.g.~\cite{HanafiT2017}).
%For a generic IP instance $I$ it is NP-hard to even decide if the set of feasible solutions $S(I)$ is empty or not.
%There are a number of heuristics for this purpose, such as the
These heuristics, such as the popular Feasibility pump algorithm \cite{fp1,fp2}, are often effective and fast in practice. However, the heuristics can sometimes fail to find a feasible solution. Moreover, these heuristics do not provide any bounds on the quality of the solution they find.

@@

>>>>

It is  NP-hard even to determine if an IP instance has a feasible solution~\cite{GareyJohnson}. Given its practical importance, however, there are many commercial (e.g. CPLEX, GUROBI, XPRESS) and free (e.g. CBC) solvers that for specific IP instances can often find solutions that are optimal within a given tolerance. Still there are known moderate-sized IP instances that no commercial solver can currently solve \cite{MIPLIB}. Thus there is value in heuristics to find feasible solutions for general IP instances (see e.g.~\cite{HanafiT2017}).
%For a generic IP instance $I$ it is NP-hard to even decide if the set of feasible solutions $S(I)$ is empty or not.
%There are a number of heuristics for this purpose, such as the
These heuristics, such as the popular Feasibility pump algorithm \cite{fp1,fp2}, are often effective and fast in practice. However, these heuristics can sometimes fail to find a feasible solution. Moreover, these heuristics do not provide any bounds on the quality of the solution they find.

@@

A keen reader might ask why Theorem \ref{domtoIP} does not imply that P = NP, as one iteratively find a feasible solution $x^*\in S(I)$, and add the constraint $x\leq cx^*-\epsilon$ for some small enough $\epsilon>0$ to $I$ until DomToIP fails to find a feasible solution. However, note that adding constraints to $I$ might result in $g(I)$ becoming infinite, in which case DomToIP would fail to find a feasible solution to the IP.
